A Computational Account of Default-Mode Function\\by Control Theory and Reinforcement Learning

### 2016-07-16 paper.tex

relevance is the critical factor that determines whether an object activates the ventral network (Downar et al., 2001). The ventral network might be considered a prime candi-date for mediating orienting to salient but unimportant stimuli, i.e., exogenous attention (Posner and Cohen, 1984), be- cause under passive conditions it is highly responsive to distinctive sensory
events in all modalities (Downar et al., 2000). The ventral network is well activated by stimuli that are important, even if they are not very distinctive. 
CURRENT OPINION: VA network does underlie  stimulus-driven reorienting to environmental stimuli based on their task relevance. An important conclusion from these neuroimaging studies is that the psychological dis- tinction between exogenous and endogenous orienting (Jo- nides, 1981) may not map onto different neural systems. "changing the control of behavior from one environ- mental input to another". Similar reorienting mechanisms may also be involved in shifting from a broad range of ‘‘internally directed’’ processes in order to deal with environmental events, as when interrupting memory retrieval (‘‘did I lock the car door?’’) to respond to a sudden stimulus (‘‘is that my cell phone ring- ing?’’). -> medites between the Default-Mode function and other more environmentally directed processing goals.

@@

>>>>

relevance is the critical factor that determines whether an object activates the ventral network (Downar et al., 2001). The ventral network might be considered a prime candi-date for mediating orienting to salient but unimportant stimuli, i.e., exogenous attention (Posner and Cohen, 1984), be- cause under passive conditions it is highly responsive to distinctive sensory
events in all modalities (Downar et al., 2000). The ventral network is well activated by stimuli that are important, even if they are not very distinctive. 
CURRENT OPINION: VA network does underlie  stimulus-driven reorienting to environmental stimuli based on their task relevance. An important conclusion from these neuroimaging studies is that the psychological dis- tinction between exogenous and endogenous orienting (Jo- nides, 1981) may not map onto different neural systems. "changing the control of behavior from one environ- mental input to another". Similar reorienting mechanisms may also be involved in shifting from a broad range of ‘‘internally directed’’ processes in order to deal with environmental events, as when interrupting memory retrieval (‘‘did I lock the car door?’’) to respond to a sudden stimulus (‘‘is that my cell phone ring- ing?’’). -> medites between the Default-Mode function and other more environmentally directed processing goals.
inducing network reconfiguration

\item
blanke:
the core region of the human vestibular cortex is situated close to the angular gyrus10. It is possible that the experience of dissociation of self from the body is a result of failure to integrate complex somatosensory and vestibular information.
Initial stimulations (n 3; 2.0–3.0 mA) induced vestibular responses, in which the patient reported that she was “sinking into the bed” or “falling from a height”.

\item
high-level social cognition also engenerded expectation violations
-> that's why coincides with "agency" meta-analytic location
(Decety 2007):
suggest that activation in the TPJ during social cognition may therefore rely on a lower-level computational mech- anism involved in generating, testing, and correcting internal predictions about external sensory events.

\item
Sridharan: RTPJ involved in bottom-up saliency detection

\item
Corbetta2002:
 We suggest that the TPJ is also strongly engaged by stimuli that are behaviourally relevant but require a change in the current task set. 
 -> exogeneously induced state transition?
 <=> MCMC in HC / PCC -> slow? endogeneous changes in state transitions by the policy and value matrices
 For example, the alarm at the museum is not part of the task set of listening to the guide’s discussion of Hieronymous Bosch, but it is clearly a behaviourally relevant stimulus.

\item
visuo- proprioceptive conflict (Balslev et al., 2005), and multi-modal detection of sensory changes (Downar et al., 2000)
brain areas connected to aRTPJ further responded to all changes of visual, auditory, or tactile stimulation in a multi-modal fMRI study (Downar et al., 2000).

\item
direct electrical stimulation of the RTPJ during neurosurgery was associated with altered perception and stimulus awareness (Blanke et al., 2002).

\item
the aRTPJ network is central for sensorimotor control by integrating supramodal stimulus-guided attention and action initia- tion during externally structured tasks.

\item
Bzdok2013

pRTPJ cluster was also functionally associated with deception tasks

qualify RTPJ as a po- tential switch between exteroceptive and interoceptive mind sets implemented by their networks. The reciprocal nature of those mind sets is well illustrated by consistent reports of continuous shifting be- tween externally (i.e., sensory) and internally (i.e., self- and presumably social/memory-) oriented processing in controlled laboratory settings and daily routine (Smallwood et al., 2007).

@@

\item
the difference between the two task groups could be parsimoniously explained by the required atten- tion to either the external world or self.
world -> policy matrix driven computation
self -> value matrix driven computation

\item
significantly reduced impact of intentions after transient TPJ disruption (Young et al. 2010b)

LTPJ:

\item
only the left TPJ was associated with language processes, whereas only the right TPJ was functionally associated with attention processes

\item 
Wernicke's area:
involved in accessing and integrating world knowlege.
involved in the comprehension or understanding of written and spoken language Damage caused to Wernicke's area results in receptive, fluent aphasia. This means that the person with aphasia will be able to fluently connect words, but the phrases will lack meaning.
A major impairment of language comprehension, while speech retains a natural-sounding rhythm and a relatively normal syntax. Language as a result is largely meaningless. difficulty finding words, putting words in the wrong order, substituting sounds and/or words, difficulty understanding spoken utterances, difficulty recognizing some words by sight, difficulty writting letters

\item a lesion study on disturbed sleep (i.e., a state of mind
independent of sensory stimulation but dependent on
internally generated information) exclusively identified
the dmPFC (Koenigs et al., 2010). Third, another VLSM study exclusively
related the IFG and TPJ, both more strongly connected to the
dmPFC in our study, to inner speech

\item
the left and right TPJ further differ according to their cytoarchitectonic borders and gyral pattern (Caspers et al., 2008; Caspers et al., 2006)
